Assessing primitives performance\\ on multi-stage execution

### 2018-05-10 paper.tex
fix one title

\paragraph{Optimization potential OR Large strings comparison performance}
The plugins come with an overhead due to the cross-file inlining and the passage through an InterpreterProxy, like said in Section \ref{sec:implem_cmp}. This is one of the factor explaining the performance gap between these versions and the Slang and Slang+JIT ones.
When it comes to comparing large strings (100 characters and more), the execution time is mainly spent in the comparison loop (Figure \ref{fig:Asm}). However, the switch overhead is still noticeable in the PureSlang implementation when strings of 100 characters are compared: PureSlang is 15.8 times faster while Slang+JIT is 16.8 times faster. This is not the case anymore on 1000-characters strings.
This last observation only applies to the GCC results. The LLVM version

>>>>

\paragraph{Optimization potential on large strings comparison}
The plugins come with an overhead due to the cross-file inlining and the passage through an InterpreterProxy, like said in Section \ref{sec:implem_cmp}. This is one of the factor explaining the performance gap between these versions and the Slang and Slang+JIT ones.
When it comes to comparing large strings (100 characters and more), the execution time is mainly spent in the comparison loop (Figure \ref{fig:Asm}). However, the switch overhead is still noticeable in the PureSlang implementation when strings of 100 characters are compared: PureSlang is 15.8 times faster while Slang+JIT is 16.8 times faster. This is not the case anymore on 1000-characters strings.
This last observation only applies to the GCC results. The LLVM version
